Multi-objective autotuning of MobileNets\\ across the full software/hardware stack

### 2018-06-11 dissemination.publication/08da9685582866a0/paper_appendix.tex
improved meta for ACM DL proceedings
added instructions how to use CK snapshot from ACM DL

Alternatively, you can install latest CK version in a user space from GitHub:
\begin{verbatim}
$ git clone http://github.com/ctuning/ck
$ export PATH=$PWD/ck/bin:$PATH
$ export PYTHONPATH=$PWD/ck:$PYTHONPATH
\end{verbatim}

\noindent Then, install CK repositories:
\begin{verbatim}
$ ck pull repo --url=https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl
$ ck pull repo:ck-tensorflow
\end{verbatim}

>>>>

Alternatively, you can install the latest CK version in a user space from GitHub:
\begin{verbatim}
$ git clone http://github.com/ctuning/ck
$ export PATH=$PWD/ck/bin:$PATH
$ export PYTHONPATH=$PWD/ck:$PYTHONPATH
\end{verbatim}

\noindent Then, install CK repositories:
\begin{verbatim}
$ ck pull repo --url=https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl
\end{verbatim}

\subsubsection{Install this CK workflow from the ACM Digital Library snapshot}

It is possible to install and test the snapshot of this workflow 
from the ACM Digital Library without interfering with your current CK installation.
Download related file "request-asplos18-artifact-?-ck-workflow.zip"
to a temporary directory, unzip it and then execute the following commands:

\begin{verbatim}
$ . ./prepare_virtual_ck.sh
$ . ./start_virtual_ck.sh
\end{verbatim}

All CK repositories will be installed in your current directory.
You can now proceed with further evaluation as described below.
